---
title: "Forest Fires in Brazil"
author: "Wensi Xu"
Date: "Dec 9th, 2019"
output: html_document
---

```{r setup, include=FALSE}
library("ggplot2")
library("dplyr")
source("analysis.R")
```

## Introduction
The dataset that I chose is a dataset about forest fires that happened in Brazil across years, containing the number of forest fires reported in Brazil by State. The series comprises a period of approximately ten years (1998 to 2017). Luis Gustavo Modelli updated the dataset to Kaggle on August 24th, 2019. He claimed that the data was obtained from the official website of the Brazilian government, and a link to the original dataset was included. This dataset was collected because Brazil has the largest rainforest in the world, which is the Amazon rainforest. By collecting and analyzing the data about the frequency of forest fire in a time series can help to take action to prevent it.

## Data graphics
```{r bar chart, echo = FALSE}
bar_chart <- graph()
print(bar_chart)
```

## Discussion
By looking at the graphs, we can conclude that most forest fires happened in 2013. From 1998 to 2003, the number of forest fires had been increasing and then decreased again. However, there was a massive increase between 2008 and 2009. And from 2009 to 2017, I do not see a trend because the total number of forest fires just fluctuated up and down.    
The stakeholders who might be influenced will be the people living around the Amazon rainforest, the animals living in the rainforest, and all human beings in the world. The people who live near the Amazon rainforest will be impacted because as the fire gets bigger, their hometown may be burnt down. The animals residing in the rainforest will be affected because the frequent fire may threaten their lives and burn all their food. All human beings will also be influenced because the Amazon rainforest is the largest rainforest in the world, meaning Amazon contributes the most to the air. It absorbs the most carbon dioxide and produces clean oxygen. Without the Amazon rainforest, global warming will be more severe, and air quality may also be worse.   
Forest fires are commonly caused by naturally occurring events, such as lighting strikes or over aridity. However, there are more and more cases that human activities can lead to forest fires, such as cropping or grazing by farmers and deforesting by loggers. These social activities probably cause more forest fires than natural events do. By understanding this dataset, we should be aware that deforesting and overgrazing may lead to severe outcomes. To save and protect the environment, we should avoid things like that.    
[News about Amazon forest fire](https://www.bbc.com/news/world-latin-america-49433767)

## Reflection
According to my analysis of the time series data, I learn that while the total number of forest fires fluctuate in recent years, there is no noticeable decrease. Many reasons may result in forest fires, such as regional drought, lightning strikes, overgrazing, or deforesting, and some events can be avoided. To decrease the number of forest fires and protect our environment, the government and also all of us should take action and try to improve our environment.   
Some new questions that I have are:

* Have the government taken any action to avoid forest fires?   
* When forest fire happens, will it be more efficient if we cut down the trees near the fire or try to put out the fire?